Scipion Tailored for TEM Facilities: Image Processing in Streaming

### 2018-02-14 2.overall.tex
w

The main change introduced in \scipion is \emph{stream processing}. Stream processing has been designed to analyze and react on real-time so that enables analysis of data as it is produced.
In this way a new level of parallelization has been reached since the  data generated by the microscope continuously flows through a chain of protocols. For example, as movies are imported to the system they are aligned and their CTF is estimated. In \scipion stable version users may find  the first steps in the image processing adapted to stream. These steps include: movie alignment and CTF estimation. In \scipion developers version all particle picking algorithm was been adapted for Streaming as well as a few 2D classification algorithms.

>>>>

The main change introduced in \scipion is \emph{stream processing}. Stream processing has been designed to analyze and react on real-time so that enables analysis of data as it is produced.
In this way a new level of parallelization has been reached since the  data generated by the microscope continuously flows through a chain of protocols. For example, as movies are imported to the system they are aligned and their CTF is estimated. In \scipion stable version users may find  the first steps in the image processing adapted to stream. These steps include: movie alignment, CTF estimation and particle picking. In \scipion developers version all several 2D classification algorithms algorithms are available.
